Deciding to Disclose

### 2015-09-14 Methods.tex
Align
Add random seed footnote

Two key measures were used: the fraction of the subpopulation who had ever signalled honestly, and the proportion referred. Both measures were taken after every round of play, and were taken relative to the agent's position in their sequence of appointments giving the probability of signalling honestly, or being referred having had a given number of appointments.

\begin{table}[h!]
\caption{Model parameters.} 
\label{tab:qt_params}
\begin{tabular} {llc}
\hline\noalign{\smallskip}
Name & Description & Value \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(n_{w}\) & Number of women & 1000 \\ 
\(n_{m}\) & Number of midwives & 100 \\ 
\(r_{m}\) & Number of appointments per midwife & 1000 \\ 
\(r_{w}\) & Maximum number of appointments per woman & 12 \\ 
Runs & Simulation runs & 1000 \\ 
\(p_{w}(h)\) & Proportion of heavy drinkers & \(1/3\) \\ 
\(p_{w}(m)\) & Proportion of moderate drinkers & \(1/3\) \\ 
\(p_{w}(l)\) & Proportion of light drinkers & \(1/3\) \\ 
\(p_{m}(h)\) & Proportion of harsh midwives & \(5/100\) \\ 
\(p_{m}(m)\) & Proportion of moderate midwives & \(10/100\) \\ 
\(p_{m}(l)\) & Proportion of non-judgemental midwives & \(85/100\) \\ 
\(q_{w}\) & Probability of women sharing & 0. \\ 
\(w_{w}\) & Weight of shared information for women & 0. \\ 
\(q_{m}\) & Probability of midwives sharing & 0. \\ 
\(w_{m}\) & Weight of shared information for midwives & 0. \\ 
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 10:1 \\ 
\(\gamma\) & Probability weighting for gains  & 0.61 \\ 
\(\delta\) & Probability weighting for losses &  0.69\\ 
\(\alpha\) & Power for gains  & 0.88 \\ 
\(\beta\) & Power for losses & 0.88 \\ 
\(\lambda\) & Loss aversion &  2.25 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

@@

Parameters for training were generated in R \citep{RTeam2014} using and appropriately transformed Latin Hypercube Sample \citep{Carnell2012} over the space of parameters given in table \ref{tab:sa_params}, giving eleven free parameters which were treated as uniformly distributed in the range given.  Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each, with emulator quality assessed by leave-one-out cross validation. A fixed set of 100 random seeds was used, such that each parameter set was run once with each seed, for every decision rule.

>>>>

Two key measures were used: the fraction of the subpopulation who had ever signalled honestly, and the proportion of the population who were referred. Both measures were taken after every round of play, and were taken relative to the agent's position in their sequence of appointments giving the probability of signalling honestly, or being referred having had a given number of appointments.

\begin{table}[h!]
\caption{Model parameters.} 
\label{tab:qt_params}
\begin{tabular} {lll}
\hline\noalign{\smallskip}
Name & Description & Value \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(n_{w}\) & Number of women & 1000 \\ 
\(n_{m}\) & Number of midwives & 100 \\ 
\(r_{m}\) & Number of appointments per midwife & 1000 \\ 
\(r_{w}\) & Maximum number of appointments per woman & 12 \\ 
Runs & Simulation runs & 1000 \\ 
\(p_{w}(h)\) & Proportion of heavy drinkers & \(1/3\) \\ 
\(p_{w}(m)\) & Proportion of moderate drinkers & \(1/3\) \\ 
\(p_{w}(l)\) & Proportion of light drinkers & \(1/3\) \\ 
\(p_{m}(h)\) & Proportion of harsh midwives & \(5/100\) \\ 
\(p_{m}(m)\) & Proportion of moderate midwives & \(10/100\) \\ 
\(p_{m}(l)\) & Proportion of non-judgemental midwives & \(85/100\) \\ 
\(q_{w}\) & Probability of women sharing & 0. \\ 
\(w_{w}\) & Weight of shared information for women & 0. \\ 
\(q_{m}\) & Probability of midwives sharing & 0. \\ 
\(w_{m}\) & Weight of shared information for midwives & 0. \\ 
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 10:1 \\ 
\(\gamma\) & Probability weighting for gains  & 0.61 \\ 
\(\delta\) & Probability weighting for losses &  0.69\\ 
\(\alpha\) & Power for gains  & 0.88 \\ 
\(\beta\) & Power for losses & 0.88 \\ 
\(\lambda\) & Loss aversion &  2.25 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

@@

Parameters for training were generated in R \citep{RTeam2014} using and appropriately transformed Latin Hypercube Sample \citep{Carnell2012} over the space of parameters given in table \ref{tab:sa_params}, giving eleven free parameters which were treated as uniformly distributed in the range given.  Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each, with emulator quality assessed by leave-one-out cross validation. A fixed set of 100 random seeds was used\footnote{Fixed random seeds were used to allow simulation results to be reproducible, since the combination of a parameter set and a random seed yields a deterministic process.}, such that each parameter set was run once with each seed, for every decision rule.
